Exploring the conformational dynamics of alanine dipeptide in solution subjected to an external electric field: A nonequilibrium molecular dynamics simulation

### 2014-02-24 writedown/npt-neq/alanine.tex
change to the paper and add reply

@@

\subsection{System settings and simulation protocol}
The system is set up in a $2.7\times 2.7\times
2.7\, \textsf{nm}^3$ periodic simulation region, with one alanine dipeptide
described by the CHARMM27 force field~\cite{foloppe2000all}, and dissolved in 644 TIP3P~\cite{jorgensen1983comparison}
water molecules.  \recheck{The grid-based energy correction map (CMAP)~\cite{mackerell2004extending}
for the backbone dihedral angles is also taken into consider.}
%The EF exserts force $\vect F = q \vect E(t)$ on
%the partial charge $q$ in the system.
The size of the  dynamical region is $R_{ex} = 1.0$~nm.
All simulations are performed by a home-modified GROMACS~4.5~\cite{pronk2013gromacs} with support to the CHARMM
force field~\cite{bjelkmar2010implementation}.
First, an equilibrium NVT simulation at 300~K of
100~\textsf{ns} was performed with a Langevin thermostat (time-scale
$\tau_T = 0.5~\textsf{ps}$).  Along the trajectory, configurations were taken every
50~\textsf{ps} and we used 2000 initial configurations for each nonequilibrium
MD simulation (if not stated otherwise for specific cases).
The branching trajectories were integrated by the
Leap-frog scheme with the aforementioned nonequilibrium
temperature control technique.  The
time step was $\Delta t = 0.002~\textsf{ps}$.
\recheck{The short-range
interaction (van der Waals interaction)
had the cut-off radius of 1.0~nm, and was smoothed from $0.8$ to $1.0$~nm by the
``switch'' method provided by GROMACS.
A energy conserving particle mesh Ewald method (PME)~\cite{darden1993pme, essmann1995spm}
method was applied to calculate the electrostatic interaction in this
periodic system. The the direct space part of PME was cut-offed and smoothed in the
same way as the van der Waals interaction.}
\recheck {All hydrogen involving bonds are constrained by LINCS~\cite{hess1997lincs}, expect that
  the TIP3P water molecules are constrained by SETTLE algorithm~\cite{miyamoto2004settle}.}
In the thermostated region, the original dynamics was
coupled to a Langevin thermostat with $\tau_T = 0.1~\textsf{ps}$.
  In all testing cases, this local thermostat is able to control
  the system at the desired temperature, i.e.~300~K (the results
  are not presented in this paper).
The whole system is also coupled to a Parrinello-Rahman barostat~\cite{parrinello1981polymorphic} with $\tau_P = 2.0~\textsf{ps}$ to keep
the pressure at ambient condition (1~Bar). Since the
change of the system size is small and slow, the pressure control
does not have an sizable effect on the
dynamics of the system.
At time $t=0$~ps, the system
has been fully equilibrated without any EF. From $t=0$ to
the warm-up time $t=t_{\textrm{warm}}$, the EF is switched on linearly, while
after $t=t_{\textrm{warm}}$, the field is kept constant in time at
$E_{\infty}$.  In this work we consider $t_{\textrm{warm}} = 10$~ps,
and $E_{\infty} = 1$~V/nm.
The direction of the field is arbitrarily chosen along the
$x$ direction.
In this paper we denote the
EF as a function of time $\vect E(t)$.
Therefore, for the case of constant EF, we have
$\vect E(t) = (E_\infty\cdot t/t_{warm},0,0)$ for $0\leq t < t_{warm}$, and 
$\vect E(t) = (E_\infty,0,0)$
for $t \geq t_{warm}$.

@@

\begin{figure}
  \centering
  \includegraphics[width=1.00\textwidth]{fig-all.eps}
  % \raisebox{0.2\height}{\includegraphics[width=0.22\textwidth]{c-2.eps}}
  % \includegraphics[width=0.37\textwidth]{fig-begin-1.eps}
  % \includegraphics[width=0.37\textwidth]{fig-end-1.eps}
  \caption{
    The probability density of the conformations of the alanine dipeptide plotted on the Ramachandran plot.
    (a): Two dihedral angles
    $\phi$ and $\psi$ are used to represent the molecular conformations of the alanine dipeptide.
    (b): The equilibrium probability density 
    at $t=0$~\textsf{ps}. (c): The probability density of equilibrium at $t=1000$~\textsf{ps}, resulting from the application of a constant EF of 1~V/nm. Darker color
    indicates higher probability.
    Plots are divided into 5 subregions corresponding
    to 5 molecular conformations:
    $A_1 = \{(\phi, \psi) | -134^\circ \leq \phi <  13^\circ, -125^\circ \leq \psi < 74^\circ\}$,
    $A_2 = \{(\phi, \psi) |  128^\circ \leq \phi < 226^\circ, -125^\circ \leq \psi < 74^\circ\}$,
    $B_1 = \{(\phi, \psi) | -110^\circ \leq \phi <  13^\circ,   74^\circ \leq \psi < 235^\circ\}$,
    $B_2 = \{(\phi, \psi) |  128^\circ \leq \phi < 250^\circ,   74^\circ \leq \psi < 235^\circ\}$,
    $C   = \{(\phi, \psi) |   13^\circ \leq \phi < 128^\circ, -180^\circ \leq \psi < 180^\circ\}$.
    Considering the angular periodicity, the angle, for example, $226^\circ$ corresponds to $-134^\circ$
    on the plot (b) and (c).
    % Considering the angular periodicity, if we write, for example,
    % $128^\circ \leq \phi <-134^\circ$, it implies that $\phi$ is in a range of $98$ degrees, between $128^\circ$ and $226^\circ$ ($226^\circ$ correspond to $-134^\circ$).
    This division is the same for both plot (b) and (c).
  }
  \label{fig:tmp4}
\end{figure}

The change of conformation in time of the alanine dipeptide is
investigated by analyzing the probability density $p(\phi,\psi,t)$ on
the Ramachandran plot at time $t$. The definition of the dihedral
angles $\phi$ and $\psi$ is given in Fig.~\ref{fig:tmp4}~(a).
The probability density of conformations of equilibrium in absence of external field is shown in Fig.~\ref{fig:tmp4}~(b), while the same quantity, resulting from the molecular relaxation to the action of $E_{\infty} = 1$~V/nm is
given in Fig.~\ref{fig:tmp4}~(c). In the plot one can identify several clusters
in which conformations are grouped.
Therefore, in order to simplify the analysis, we divide the
Ramachandran plot into 5 subregions $\{A_1, A_2, B_1, B_2, C\}$
(see caption of Fig.~\ref{fig:tmp4} for the corresponding definition).
It is worth to notice that these conformations
are found in different secondary structures of a peptide chain:
$A_1$ and $A_2$ are
corresponding to the $\alpha$-helix. $B_1$ and $B_2$ are
corresponding to the $\beta$-sheet. $C$ is corresponding to the
left-handed $\alpha$-helix.

From Fig.~\ref{fig:tmp4}, it is evident that the probability with which a
conformation occurs changes when the external EF is applied.
The most evident case is conformation $C$; in fact it is {almost} not present before the external field is applied but appears in a clear way as a response to the action of the EF. Following this line of thought, we are interested to study the change of conformation under the action of EF. Specifically, for each conformational change, we will analyze the relation between the structural relaxation of the molecule and its corresponding time scale. 
The starting point is the calculation of the probability
of each conformation:
\begin{align}
  P_I(t) = \mathbb P ( (\phi_t,\psi_t) \in I), \quad  I \in \{A_1, A_2, B_1, B_2, C\},
\end{align}
Notice that the probability is time dependent, being an observable in nonequilibrium situation.
Next,
we consider the net probability flux from conformation $I$ to $J$, defined by:
\begin{align}\nonumber
  F_{J,I}(t) & = \frac1{\Delta t}\,
  \bigg[\,
  \mathbb P \big( (\phi_{t-\Delta t},\psi_{t-\Delta t}) \in J,\, (\phi_t, \psi_t) \in I \,\big) 
  -
  \mathbb P \big( (\phi_{t-\Delta t}, \psi_{t-\Delta t}) \in I,\, (\phi_t, \psi_t) \in J \,\big)
  \bigg], \\\label{eqn:tmp7}
  & J,I \in \{A_1, A_2, B_1, B_2, C\}.
\end{align}
% {\bf Here for $\lim_{\Delta \to 0}$ is intended that in the simulation the time interval is taken large enough so that we have  enough events and thus stable numbers (see also Ref.~\cite{schuette2011markov})}.
Where $\mathbb P\big( (\phi_{t-\Delta t}, \psi_{t-\Delta t}) \in J,\, (\phi_t, \psi_t) \in I\,\big)$
is the joint probability of the alanine being in conformation $J$ at
time $(t-\Delta t)$ \emph{and} being in conformation $I$ at time $t$.
The same definition applies to
$\mathbb P \big( (\phi_{t-\Delta t}, \psi_{t-\Delta t}) \in I,\, (\phi_t, \psi_t) \in J\,\big)$.
Here the time interval $\Delta t$ should be small enough compared to the
time scale of conformational dynamics,
so that the changes in the conformation probabilities
can be treated in linear approximation.
At the same time,  $\Delta t$ should be also large enough compared with
the timestep of the MD integrator, 
so that the quantities of Eq.~\eqref{eqn:tmp7} are well-defined, and can be
estimated with sufficient numerical accuracy (see also Ref.~\cite{schuette2011markov}).
A positive value of $F_{J,I}(t)$ indicates that the
net flux goes from $J$ to $I$,
while a negative value indicates a net flux from $I$ to $J$.
Through $F_{J,I}(t)$, the analysis of the nonequilibrium process 
is projected onto the analysis of the probabilistic link between discretized conformations $\{A_1, A_2, B_1, B_2, C\}$.
In the case of oscillatory EF, the behaviour of the net probability flux is also highly oscillatory, thus, in order to clearly identify the essential features of the molecular conformational changes, it is convenient to study the integrated net probability flux, defined as:
\begin{align}\label{eqn:tmp7a}
  Q_{J,I} (t) = \int_0^t F_{J,I}(\tau)d \tau,
\end{align}
which expresses the cumulative effects due to the action of EF on the conformations of the molecule.

\recheck{ The definition of the probability flux is similar to the
  kinetic rate.  However, we want to stress that, in genarl, the
  probability flux should not be interpreted as a kinetic rate, and
  one cannot replace the nonequilibrium molecular dynamics by a
  kinetic analysis. The main reason is that the conformational
  dynamics of alanine dipeptide is generally not Markovian for a small
  time interval $\Delta t$~\cite{prinz2011markov}, therefore, a direct application of the kinetic
  analysis is questionable. Since the main goal of our research is to propose a
  nonequilibrium molecular dynamics simulation method, the numerical
  results will not be compared with a kinetic analysis.
}

@@

\begin{figure}
  \centering
  \includegraphics[]{fig.ala.new/fig-meta-npt.eps}
  \caption{The time-dependent probability of conformations $P_I(t)$ 
    when a constant EF is present, where $\sum_I P_I(t) = 1, \forall t$.
    The warm-up time is $t_{warm} = 10$~ps. The red line refers to conformation $I = A_1$,
    green to $A_2$, dark blue to $B_1$, purple to $B_2$ and light blue
    to $C$. 
  }
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-1.eps}
  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-2.eps}
  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-3.eps}
  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-4.eps}
  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-5.eps}
  \caption{
    The net probability flux for the constant EF case.
    The warm-up time is $t_{warm} = 10$~ps.
    The probability flux $F_{J,I}(t)$ (defined by Eqn.~\eqref{eqn:tmp7}) is reported in units of $\textrm{ps}^{-1}$.
    From top, left to right we report $I = A_1$, $A_2$, $B_1$; bottom, left to right $B_2$ and
    $C$, respectively. In each plot, the red line stands for $J=A_1$,
    green for $J=A_2$, dark blue for $J=B_1$, purple for $J=B_2$ and light blue
    for $J=C$.
    }
  \label{fig:tmp6}
\end{figure}

The time-dependent probability density of the system to stay in a certain
conformation is given in
Fig.~\ref{fig:tmp5}. The $\beta$-sheet conformations $B_1$ and $B_2$,
which are present at the initial stage after EF is switched on,
fade away as the system relaxes to the new equilibrium. The
probability of the $\alpha$-helix conformation $A_1$, grows from 0.45 to 0.69.
The $\alpha$-helix $A_2$  does not change significantly  under the action of EF.
The left-hand helix conformation $C$ noticeably grows from 0 to 0.22.
We plot the net probability fluxes in Fig.~\ref{fig:tmp6}.
Results show that for short $t$, the net fluxes are generally non-zero, however, 
as $t$ goes to infinity,
all fluxes converge to zero. This indicates
that as the EF is switched on, the system first is driven away from the initial
equilibrium (at zero EF);  This is a nonequilibrium process.
After a time long enough, the system
is fully relaxed to the new equilibrium defined by the action of the constant EF,
and stays there as long as the EF is kept.
An important point is that despite the system is finally relaxed to the new conformation,
the relaxation timescales corresponding to each conformation are rather different. 
From Fig.~\ref{fig:tmp5} and \ref{fig:tmp6}, we observe mainly
three different timescales 10~ps, 100~ps and 500~ps,
whose corresponding conformations are summarized in Tab.~\ref{tab:tmp1}.
This is a relevant result because it shows the possibility of employing an external EF as a tool to identify relevant time scales in the conformational behaviour of a molecule in solution.

\begin{table}
  \centering
  \begin{tabular*}{0.4\textwidth}{@{\extracolsep{\fill}}lc}\hline\hline
    Direction        & time scale [ ps ] \\\hline
    $A_1\rightarrow A_2$        &       $\sim 10$      \\
    % $B_1\rightarrow B_2$        &       $\sim 10$      \\    
    $B_2\rightarrow A_1,\ A_2,\ C$        &       $\sim 50$      \\    
    $A_2\rightarrow A_1$        &       $\sim 100$      \\
    $B_2\rightarrow B_1$        &       $\sim 100$      \\    
    $B_1\rightarrow A_1,\ C$        &       $\sim 500$      \\    \hline\hline
  \end{tabular*}
  \caption{A list of the main probability fluxes and the corresponding time scales observed in the constant EF case.}
  \label{tab:tmp1}
\end{table}

@@

The dipole moment of the alanine dipeptide is defined by
\begin{align}\label{eqn:tmp8}
  \boldsymbol\mu_{\textrm{alanine}}(t) =
  \bigg\langle
  \sum_{i\in \{\textrm{atoms of alanine}\}}
  q_i\, \vect r_i(t)
  \bigg\rangle,
\end{align}
where $q_i$ denotes the partial charge of any point particle $i$ defining our model of alanine,
the molecule being neutral, i.e.~$\sum_iq_i = 0$.
$\vect r_i$ denotes the position of the particle $i$.
Fig.~\ref{fig:tmp3}
shows that the $x$-component of the dipole moment 
reaches 85\% of its maximum value in only 20~ps, which is comparable to
the warm-up time $t_{warm}$, and is 25 times
smaller than the slowest time scale of the conformational relaxation.
Then in the following 400~ps, the dipole slowly relaxes to its 
maximum value, that is, 
6.8~Debye, and  corresponds to an energy
($\boldsymbol\mu_{\textrm{alanine}} \cdot \vect E$)
of c.a.~$-13.6$~kJ/mol.
We calculate the averaged dipole moment of different conformations
(defined by taking average in Eqn.~\eqref{eqn:tmp8}
only for a certain conformation)
under the constant EF, and they are 6.8, 6.0, 5.1, 3.1 and 7.1~Debye
for $A_1$, $A_2$, $B_1$, $B_2$ and $C$, respectively.
The dipole energy difference between 3.1 and 7.1~Debye is roughly 8.0~kJ/mol.
Under a constant EF, the system will be likely to be driven towards those
conformations with higher dipole moment, because the
energy of the system will be lowered.  We suggest that this energy difference may be the reason why
we observe that the $\beta$-sheet conformations with lower dipole moment
are driven towards $\alpha$-helix conformations
$A_1$ and $C$, whose dipole moments are the highest
among all conformations. Moreover, the $B_2$ conformation vanishes because
its dipole is significantly lower than other conformations.
Comparing Fig.~\ref{fig:tmp3} with~\ref{fig:tmp5},
  the sharp increment of dipole moment before 20~ps is due to the quick vanishing of conformation
  $B_2$, while the slow increment of dipole moment until 400~ps is due to
  the slow migration from conformation $B_1$ to $A_1$ and $C$.
  % \textit{NOTE: here we want to discuss the relation between
  %   the conformation and the dipole moment. I rewote this
  %   sentence.}
% From 0 to 20~ps, the probability of
% lowest dipole conformation $B_2$ quickly
% vanishes. We observe a sharp increment of the average molecular dipole and finally, approaching  500~ps, the conformation slowly migrates from
% $B_1$ to $A_1$ and $C$. Moreover, since the dipole moment $A_1$ and $C$
% is higher than $B_1$, the average molecular dipole moment slowly increases
% to the nonequilibrium steady value.

>>>>

\newcommand{\confaa}[0]{{\alpha_{\textrm{R}}}}
\newcommand{\confab}[0]{{\alpha_{\textrm{R}}'}}
\newcommand{\confba}[0]{{\textrm{C}7_{\textrm{eq}}}}
\newcommand{\confbb}[0]{{\textrm{C}5}}
\newcommand{\confc}[0]{{\alpha_{\textrm{L}}}}

@@

\subsection{System settings and simulation protocol}
The system is set up in a $2.7\times 2.7\times
2.7\, \textsf{nm}^3$ periodic simulation region, with one alanine dipeptide
described by the CHARMM27 force field~\cite{foloppe2000all}, and dissolved in 644 TIP3P~\cite{jorgensen1983comparison}
water molecules.  \recheck{The grid-based energy correction map (CMAP)~\cite{mackerell2004extending}
for the backbone dihedral angles is also taken into consider.}
%The EF exserts force $\vect F = q \vect E(t)$ on
%the partial charge $q$ in the system.
The size of the  dynamical region is $R_{ex} = 1.0$~nm.
All simulations are performed by a home-modified GROMACS~4.5~\cite{pronk2013gromacs} with support to the CHARMM
force field~\cite{bjelkmar2010implementation}.
First, an equilibrium NVT simulation at 300~K of
100~\textsf{ns} was performed with a Langevin thermostat (time-scale
$\tau_T = 0.5~\textsf{ps}$).  Along the trajectory, configurations were taken every
50~\textsf{ps} and we used 2000 initial configurations for each nonequilibrium
MD simulation (if not stated otherwise for specific cases).
The branching trajectories were integrated by the
Leap-frog scheme with the aforementioned nonequilibrium
temperature control technique.  The
time step was $0.002~\textsf{ps}$.
\recheck{The short-range
interaction (van der Waals interaction)
had the cut-off radius of 1.0~nm, and was smoothed from $0.8$ to $1.0$~nm by the
``switch'' method provided by GROMACS.
A energy conserving particle mesh Ewald method (PME)~\cite{darden1993pme, essmann1995spm}
method was applied to calculate the electrostatic interaction in this
periodic system. The the direct space part of PME was cut-offed and smoothed in the
same way as the van der Waals interaction.}
\recheck {All hydrogen involving bonds are constrained by LINCS~\cite{hess1997lincs}, expect that
  the TIP3P water molecules are constrained by SETTLE algorithm~\cite{miyamoto2004settle}.}
In the thermostated region, the original dynamics was
coupled to a Langevin thermostat with $\tau_T = 0.1~\textsf{ps}$.
  In all testing cases, this local thermostat is able to control
  the system at the desired temperature, i.e.~300~K (the results
  are not presented in this paper).
The whole system is also coupled to a Parrinello-Rahman barostat~\cite{parrinello1981polymorphic} with $\tau_P = 2.0~\textsf{ps}$ to keep
the pressure at ambient condition (1~Bar). Since the
change of the system size is small and slow, the pressure control
does not have an sizable effect on the
dynamics of the system.
At time $t=0$~ps, the system
has been fully equilibrated without any EF. From $t=0$ to
the warm-up time $t=t_{\textrm{warm}}$, the EF is switched on linearly, while
after $t=t_{\textrm{warm}}$, the field is kept constant in time at
$E_{\infty}$.  In this work we consider $t_{\textrm{warm}} = 10$~ps,
and $E_{\infty} = 1$~V/nm.
The direction of the field is arbitrarily chosen along the
$x$ direction.
In this paper we denote the
EF as a function of time $\vect E(t)$.
Therefore, for the case of constant EF, we have
$\vect E(t) = (E_\infty\cdot t/t_{warm},0,0)$ for $0\leq t < t_{warm}$, and 
$\vect E(t) = (E_\infty,0,0)$
for $t \geq t_{warm}$.

@@

\begin{figure}
  \centering
  \includegraphics[width=1.00\textwidth]{fig.ala.new/fig.all/fig-all.eps}
  % \raisebox{0.2\height}{\includegraphics[width=0.22\textwidth]{c-2.eps}}
  % \includegraphics[width=0.37\textwidth]{fig-begin-1.eps}
  % \includegraphics[width=0.37\textwidth]{fig-end-1.eps}
  \caption{
    The probability density of the conformations of the alanine dipeptide plotted on the Ramachandran plot.
    (a): Two dihedral angles
    $\phi$ and $\psi$ are used to represent the molecular conformations of the alanine dipeptide.
    (b): The equilibrium probability density 
    at $t=0$~\textsf{ps}. (c): The probability density of equilibrium at $t=1000$~\textsf{ps}, resulting from the application of a constant EF of 1~V/nm. Darker color
    indicates higher probability.
    Plots are divided into 5 subregions corresponding
    to 5 molecular conformations:
    $\confaa = \{(\phi, \psi) | -134^\circ \leq \phi <  13^\circ, -125^\circ \leq \psi < 74^\circ\}$,
    $\confab = \{(\phi, \psi) |  128^\circ \leq \phi < 226^\circ, -125^\circ \leq \psi < 74^\circ\}$,
    $\confba = \{(\phi, \psi) | -110^\circ \leq \phi <  13^\circ,   74^\circ \leq \psi < 235^\circ\}$,
    $\confbb = \{(\phi, \psi) |  128^\circ \leq \phi < 250^\circ,   74^\circ \leq \psi < 235^\circ\}$,
    $\confc   = \{(\phi, \psi) |   13^\circ \leq \phi < 128^\circ, -180^\circ \leq \psi < 180^\circ\}$.
    Considering the angular periodicity, the angle, for example, $226^\circ$ corresponds to $-134^\circ$
    on the plot (b) and (c).
    % Considering the angular periodicity, if we write, for example,
    % $128^\circ \leq \phi <-134^\circ$, it implies that $\phi$ is in a range of $98$ degrees, between $128^\circ$ and $226^\circ$ ($226^\circ$ correspond to $-134^\circ$).
    This division is the same for both plot (b) and (c).
  }
  \label{fig:tmp4}
\end{figure}

The change of conformation in time of the alanine dipeptide is
investigated by analyzing the probability density $p(\phi,\psi,t)$ on
the Ramachandran plot at time $t$. The definition of the dihedral
angles $\phi$ and $\psi$ is given in Fig.~\ref{fig:tmp4}~(a).
The probability density of conformations of equilibrium in absence of external field is shown in Fig.~\ref{fig:tmp4}~(b), while the same quantity, resulting from the molecular relaxation to the action of $E_{\infty} = 1$~V/nm is
given in Fig.~\ref{fig:tmp4}~(c). In the plot one can identify several clusters
in which conformations are grouped.
Therefore, in order to simplify the analysis, we divide the
Ramachandran plot into 5 subregions $\{\confaa, \confab, \confba, \confbb, \confc\}$
(see caption of Fig.~\ref{fig:tmp4} for the corresponding definition).
It is worth to notice that these conformations
are found in different secondary structures of a peptide chain:
$\confaa$ and $\confab$ are
corresponding to the $\alpha$-helix. $\confba$ and $\confbb$ are
corresponding to the $\beta$-sheet. $\confc$ is corresponding to the
left-handed $\alpha$-helix.

From Fig.~\ref{fig:tmp4}, it is evident that the probability with which a
conformation occurs changes when the external EF is applied.
The most evident case is conformation $\confc$; in fact it is {almost} not present before the external field is applied but appears in a clear way as a response to the action of the EF. Following this line of thought, we are interested to study the change of conformation under the action of EF. Specifically, for each conformational change, we will analyze the relation between the structural relaxation of the molecule and its corresponding time scale. 
The starting point is the calculation of the probability
of each conformation:
\begin{align}
  P_I(t) = \mathbb P ( (\phi_t,\psi_t) \in I), \quad  I \in \{\confaa, \confab, \confba, \confbb, \confc\},
\end{align}
Notice that the probability is time dependent, being an observable in nonequilibrium situation.
Next,
we consider the net probability flux from conformation $I$ to $J$, defined by:
\begin{align}\nonumber
  F_{J,I}(t) & = \frac1{\Delta t}\,
  \bigg[\,
  \mathbb P \big( (\phi_{t-\Delta t},\psi_{t-\Delta t}) \in J,\, (\phi_t, \psi_t) \in I \,\big) 
  -
  \mathbb P \big( (\phi_{t-\Delta t}, \psi_{t-\Delta t}) \in I,\, (\phi_t, \psi_t) \in J \,\big)
  \bigg], \\\label{eqn:tmp7}
  & J,I \in \{\confaa, \confab, \confba, \confbb, \confc\}.
\end{align}
% {\bf Here for $\lim_{\Delta \to 0}$ is intended that in the simulation the time interval is taken large enough so that we have  enough events and thus stable numbers (see also Ref.~\cite{schuette2011markov})}.
Where $\mathbb P\big( (\phi_{t-\Delta t}, \psi_{t-\Delta t}) \in J,\, (\phi_t, \psi_t) \in I\,\big)$
is the joint probability of the alanine being in conformation $J$ at
time $(t-\Delta t)$ \emph{and} being in conformation $I$ at time $t$.
The same definition applies to
$\mathbb P \big( (\phi_{t-\Delta t}, \psi_{t-\Delta t}) \in I,\, (\phi_t, \psi_t) \in J\,\big)$.
Here the time interval $\Delta t$ should be small enough compared to the
time scale of conformational dynamics,
so that the changes in the conformation probabilities
can be treated in linear approximation.
At the same time,  $\Delta t$ should be also large enough compared with
the timestep of the MD integrator, 
so that the quantities of Eq.~\eqref{eqn:tmp7} are well-defined, and can be
estimated with sufficient numerical accuracy (see also Ref.~\cite{schuette2011markov}).
\recheck{In all the numerical examples of this work, $\Delta t = 1$~ps is used}.
A positive value of $F_{J,I}(t)$ indicates that the
net flux goes from $J$ to $I$,
while a negative value indicates a net flux from $I$ to $J$.
Through $F_{J,I}(t)$, the analysis of the nonequilibrium process 
is projected onto the analysis of the probabilistic link between discretized conformations $\{\confaa, \confab, \confba, \confbb, \confc\}$.

\recheck{ The definition of the probability flux is similar to the
  kinetic rate.  However, we want to stress that, in general, the
  probability flux should not be interpreted as a kinetic rate, and
  one cannot replace the nonequilibrium molecular dynamics by a
  kinetic analysis. The main reason is, firstly, that the nonequilibrium
  nature of the problem asks for a small time interval $\Delta t$ so that the probability flux is well defined.
  Secondly, within the small
  time interval (we use 1~ps), the conformational
  dynamics of alanine dipeptide is generally not Markovian~\cite{schuette2011markov, prinz2011markov},
  therefore, a direct application of the kinetic
  analysis is questionable.
  % Since the main goal of our research is to propose a
  % nonequilibrium molecular dynamics simulation method, the numerical
  % results will not be compared with the kinetic analysis.
}

In the case of oscillatory EF, the behaviour of the net probability flux is also highly oscillatory, thus, in order to clearly identify the essential features of the molecular conformational changes, it is convenient to study the integrated net probability flux, defined as:
\begin{align}\label{eqn:tmp7a}
  Q_{J,I} (t) = \int_0^t F_{J,I}(\tau)d \tau,
\end{align}
which expresses the cumulative effects due to the action of EF on the conformations of the molecule.

@@

\begin{figure}
  \centering
  \includegraphics[]{fig.ala.new/fig-meta-more.eps}
  \caption{The time-dependent probability of conformations $P_I(t)$ 
    when a constant EF is present, where $\sum_I P_I(t) = 1, \forall t$.
    The warm-up time is $t_{warm} = 10$~ps. The red line refers to conformation $I = \confaa$,
    green to $\confab$, dark blue to $\confba$, purple to $\confbb$ and light blue
    to $\confc$. \recheck{
      The solid lines denote the results of one branching trajectory
      starting from each initial conformation, while the dashed lines denote
      the results of four branching trajectories (different random seeds for the Langevin thermostat) starting from each initial
      conformation.
      The shadow region with each solid line denotes the
      statistical uncertainty of the result at 95\% confidence level.
    }
  }
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-1.eps}
  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-2.eps}
  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-3.eps}
  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-4.eps}
  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-5.eps}
  \caption{
    The net probability flux for the constant EF case.
    The warm-up time is $t_{warm} = 10$~ps.
    The probability flux $F_{J,I}(t)$ (defined by Eqn.~\eqref{eqn:tmp7}) is reported in units of $\textrm{ps}^{-1}$.
    From top, left to right we report $I = \confaa$, $\confab$, $\confba$; bottom, left to right $\confbb$ and
    $\confc$, respectively. In each plot, the red line stands for $J=\confaa$,
    green for $J=\confab$, dark blue for $J=\confba$, purple for $J=\confbb$ and light blue
    for $J=\confc$.
    }
  \label{fig:tmp6}
\end{figure}

The time-dependent probability density of the system to stay in a certain
conformation is given in
Fig.~\ref{fig:tmp5}.
\recheck{The simulation results of starting one branching trajectory
  from each initial conformation are compared with those starting
  four branching trajectories from each initial conformation (each with
  different random seed for the Langevin thermostat).
  They are consistent within the statistical uncertainty, which
  means our simulation result is robust with respect to the randomness
  introduced by the (local) Langevin thermostat.
}
The $\beta$-sheet conformations $\confba$ and $\confbb$,
which are present at the initial stage after EF is switched on,
\recheck{fade away as the system relaxes}. The
probability of the $\alpha$-helix conformation $\confaa$, grows from 0.45 to 0.69.
The $\alpha$-helix $\confab$  does not change significantly  under the action of EF.
The left-hand helix conformation $\confc$ noticeably grows from 0 to 0.22.
We plot the net probability fluxes in Fig.~\ref{fig:tmp6}.
Results show that for short $t$, the net fluxes are generally non-zero,
however, 
as $t$ goes to infinity,
all fluxes converge to zero. This indicates
that as the EF is switched on, the system first is driven away from the initial
equilibrium (at zero EF);  This is a nonequilibrium process.
\recheck{After a time long enough, the system
is fully relaxed to the new conformations,
and stays there as long as the EF is kept. However, whether the new conformations
are in the new equilibrium defined the constant EF is not clear, because
there may exist very slow nonequilibrium processes, for example as long as 1~$\mu$s,
which cannot be discovered by our nonequilibrium simulation of only 1~ns.
What we can do by the proposed nonequilibrium simulation
method is to study time-dependent behaviours that are no longer than
the simulation time. 
}
% After a time long enough, the system
% is fully relaxed to the new equilibrium defined by the action of the constant EF,
% and stays there as long as the EF is kept.
An important point is that despite the system is finally relaxed to the new conformation,
the relaxation timescales corresponding to each conformation are rather different. 
From Fig.~\ref{fig:tmp5} and \ref{fig:tmp6}, we observe mainly
three different timescales 10~ps, 100~ps and 500~ps,
whose corresponding conformations are summarized in Tab.~\ref{tab:tmp1}.
This is a relevant result because it shows the possibility of employing an external EF as a tool to identify relevant time scales in the conformational behaviour of a molecule in solution.

\begin{table}
  \centering
  \begin{tabular*}{0.4\textwidth}{@{\extracolsep{\fill}}lc}\hline\hline
    Direction        & time scale [ ps ] \\\hline
    $\confaa\rightarrow \confab$        &       $\sim 10$      \\
    % $\confba\rightarrow \confbb$        &       $\sim 10$      \\    
    $\confbb\rightarrow \confaa,\ \confab,\ \confc$        &       $\sim 50$      \\    
    $\confab\rightarrow \confaa$        &       $\sim 100$      \\
    $\confbb\rightarrow \confba$        &       $\sim 100$      \\    
    $\confba\rightarrow \confaa,\ \confc$        &       $\sim 500$      \\    \hline\hline
  \end{tabular*}
  \caption{A list of the main probability fluxes and the corresponding time scales observed in the constant EF case.}
  \label{tab:tmp1}
\end{table}

@@

The dipole moment of the alanine dipeptide is defined by
\begin{align}\label{eqn:tmp8}
  \boldsymbol\mu_{\textrm{alanine}}(t) =
  \bigg\langle
  \sum_{i\in \{\textrm{atoms of alanine}\}}
  q_i\, \vect r_i(t)
  \bigg\rangle,
\end{align}
where $q_i$ denotes the partial charge of any point particle $i$ defining our model of alanine,
the molecule being neutral, i.e.~$\sum_iq_i = 0$.
$\vect r_i$ denotes the position of the particle $i$.
Fig.~\ref{fig:tmp3}
shows that the $x$-component of the dipole moment 
reaches 85\% of its maximum value in only 20~ps, which is comparable to
the warm-up time $t_{warm}$, and is 25 times
smaller than the slowest time scale of the conformational relaxation.
Then in the following 400~ps, the dipole slowly relaxes to its 
maximum value, that is, 
6.8~Debye, and  corresponds to an energy
($\boldsymbol\mu_{\textrm{alanine}} \cdot \vect E$)
of c.a.~$-13.6$~kJ/mol.
We calculate the averaged dipole moment of different conformations
(defined by taking average in Eqn.~\eqref{eqn:tmp8}
only for a certain conformation)
under the constant EF, and they are 6.8, 6.0, 5.1, 3.1 and 7.1~Debye
for $\confaa$, $\confab$, $\confba$, $\confbb$ and $\confc$, respectively.
The dipole energy difference between 3.1 and 7.1~Debye is roughly 8.0~kJ/mol.
Under a constant EF, the system will be likely to be driven towards those
conformations with higher dipole moment, because the
energy of the system will be lowered.  We suggest that this energy difference may be the reason why
we observe that the $\beta$-sheet conformations with lower dipole moment
are driven towards $\alpha$-helix conformations
$\confaa$ and $\confc$, whose dipole moments are the highest
among all conformations. Moreover, the $\confbb$ conformation vanishes because
its dipole is significantly lower than other conformations.
Comparing Fig.~\ref{fig:tmp3} with~\ref{fig:tmp5},
  the sharp increment of dipole moment before 20~ps is due to the quick vanishing of conformation
  $\confbb$, while the slow increment of dipole moment until 400~ps is due to
  the slow migration from conformation $\confba$ to $\confaa$ and $\confc$.
  % \textit{NOTE: here we want to discuss the relation between
  %   the conformation and the dipole moment. I rewote this
  %   sentence.}
% From 0 to 20~ps, the probability of
% lowest dipole conformation $\confbb$ quickly
% vanishes. We observe a sharp increment of the average molecular dipole and finally, approaching  500~ps, the conformation slowly migrates from
% $\confba$ to $\confaa$ and $\confc$. Moreover, since the dipole moment $\confaa$ and $\confc$
% is higher than $\confba$, the average molecular dipole moment slowly increases
% to the nonequilibrium steady value.
